Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

\vspace{1ex}\noindent\textbf{Issue \#2,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc{}. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.

>>>>

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc{}. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.
